---
title: "DSE3101 Backend Technical Report"
author: "niyun"
date: "2024-04-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This report aims to provide a technical analysis of the back-end code of tourist attraction discovery dashboard. 

As a guide, the main code chunk supporting back-end operations is named ‘backend_code.R’ in Github. 

The local datasets that we have collated and stored in Github include ‘Bus_stops_wroutes.csv’, ‘Singapore Tourist Attractions.csv’, ‘bus_routes.csv’, ‘bus_stops.csv’, ‘food_locations.csv’, food_locations_wcoords.csv’, ‘tourist_locations_wproximalbusstops.csv’. We rely on manipulating these datasets to return the eventual results to the user. 

```{r Libraries}
library(readr)
library(httr)
library(geosphere)
library(jsonlite)
library(lubridate)
library(tidyr)
library(tidyverse)
library(readxl)
library(fuzzyjoin)
```

```{r Setting Up APIs and tokens}
current_dir <- getwd()

tokens_dir <- file.path(current_dir, "Tokens")
datasets_dir <- file.path(current_dir, "Datasets")

api_key_filepath <- file.path(tokens_dir, "lta_api_token.csv")
api_key_file <- read_csv(api_key_filepath)
api_key <- api_key_file$AccountKey
headers <- c(AccountKey = api_key)

bus_stops_filepath <- file.path(datasets_dir, "bus_stops.csv")
bus_stops_file_exists <- file.exists(bus_stops_filepath)
```

As the team used Jay’s personal food blog account (Instagram: @pandareviewsfood) for delicacies recommendations, we also manipulated Instagram tokens to store the information in a local csv file for ease of manipulation. The backend team also filtered for only ratings equal to or above 7 to give our users a pleasant dining experience. 

```{r Instagram Tokens}
ig_token_key_filepath <- file.path(tokens_dir, "ig_token.csv")
ig_token_file_exists <- file.exists(ig_token_key_filepath)
client_secret_filepath <- file.path(tokens_dir, "ig_client_secret.csv")
client_secret_token_file <- read_csv(client_secret_filepath)
client_secret <- client_secret_token_file$SecretCode

if (!ig_token_file_exists) {
  ### Instagram API
  code <- "AQADhvoWdu482cDGfQocmNrSry7rh4sH7a0bhLojRoSawjZ0zB0eL5JnH-E-SpY5oWtDojARxK2s_QZmQwaagiABS9W4sO5gqZ1xZ3k1_hn5Jnlj3d4f1W2pEbl4cei8neDAzxJ48Df-uOswufuYxencxTbF61uJVL1z85-6UEYnbQ7Zw4Jk8-ZBhsQZMV7VEemGFTgTBWldLLCflAnpavXZz1DpNG_ZzrnENcmS93R0YA"

  params <- list(
    client_id = "1074040483264515", client_secret = client_secret, code = code,
    grant_type = "authorization_code", redirect_uri = "https://jiakaihoo.wixsite.com/pandacon"
  )

  ### Short_lived token
  request <- POST(url = "https://api.instagram.com/oauth/access_token", body = params)
  requestJSON <- content(request)
  short_lived_access_token <- requestJSON$access_token

  ### Long_lived token
  params <- list(
    access_token = short_lived_access_token, client_secret = client_secret,
    grant_type = "ig_exchange_token"
  )

  request <- GET(url = "https://graph.instagram.com/access_token", query = params)
  requestJSON <- content(request)
  long_lived_access_token <- requestJSON$access_token
  current_time <- format(Sys.time(), "%Y-%m-%d %H:%M:%S")
  token_df <- data.frame(
    access_token = c(long_lived_access_token),
    time = current_time
  )
  ## Writing to csv file
  write.csv(token_df, ig_token_key_filepath, row.names = FALSE)
} else {
  print("File exists")
}

ig_token_file <- read_csv(ig_token_key_filepath)
ig_token <- ig_token_file$access_token

### Retrieval of locations
food_locations_file_name <- file.path(datasets_dir, "food_locations.csv")
food_locations_file_name_exists <- file.exists(food_locations_file_name)

if (!food_locations_file_name_exists) {
  params <- list(access_token = token, fields = "id,caption,media_url,permalink,timestamp")
  food_df <- data.frame()

  request <- GET(url = "https://graph.instagram.com/me/media", query = params)
  requestJSON <- content(request)
  temp_df <- do.call(rbind, lapply(requestJSON$data, as.data.frame))
  food_df <- rbind(food_df, temp_df)

  # params = list(access_token = token, fields = 'id,media_url,permalink,timestamp')
  # request <- GET(url = 'https://graph.instagram.com/17966518561288167/children', query = params)
  # requestJSON <- content(request)
  # temp_df = do.call(rbind, lapply(requestJSON$data, as.data.frame))
  # food_df = rbind(food_df, temp_df)

  ## Loops using the API [The next link is tagged in the JSON if it exists]
  while (TRUE) {
    if (!is.null(requestJSON$paging$`next`)) {
      print(requestJSON$paging$`next`)
      request <- GET(url = requestJSON$paging$`next`)
      requestJSON <- content(request)
      temp_df <- do.call(rbind, lapply(requestJSON$data, as.data.frame))

      food_df <- rbind(food_df, temp_df)
    } else {
      break
    }
  }

  ## Filter for only ratings >=7 and removes unnecessary food reviews
  above_7 <- sapply(food_df$caption, function(row) {
    ### Non-wanted cause of various reasons, i.e. cheap/closed/private dining
    phrases <- c(
      "Chagee", "Evviva", "Sakeya", "Chaffic", "\\{Closed\\}", "Heytea", "HEYTEA", "Fruce", "Whale Tea", "\\[Delivery\\]",
      "Pots and Pans", "Fragrance", "Fardello", "CHICHA"
    )
    match <- str_extract(row, ":\\s\\d")
    if (is.na(match)) {
      return(FALSE) # If ":" is not found
    } else {
      test_int <- substr(match, nchar(match), nchar(match))
      # Extract the substring after the first ":"
      # Check if the number is greater than 7
      if (test_int >= 7) {
        if (str_detect(row, paste(phrases, collapse = "|"))) {
          return(FALSE)
        } else {
          return(TRUE)
        }
      } else {
        return(FALSE)
      }
    }
  })

  ## Modifications of the dataframe to be stored so it can be merged with the rest of the attractions
  wanted_food_df <- food_df[above_7, ]
  wanted_food_df_destination <- sapply(wanted_food_df$caption, function(row) {
    destination <- str_extract(row, str_extract(row, "^[^[:\\[\\]]]+"))
    return(destination)
  })
  wanted_food_df$destination <- wanted_food_df_destination
  wanted_food_df$type <- "food"
  wanted_food_df$"latitude & longitude" <- NA
  wanted_food_df <- wanted_food_df[, c("destination", "type", "latitude & longitude", "permalink", "timestamp", "id")]

  # Save the result
  write.csv(wanted_food_df, food_locations_file_name, row.names = FALSE)
} else {
  print("File exists")
}

food_locations <- read_csv(food_locations_file_name)

## Manually add coordinates for location
food_locations_wcoords_filepath <- file.path(datasets_dir, "food_locations_wcoords.csv")
food_locations_mod <- read_csv(food_locations_wcoords_filepath)
```

```{r Total Attractions}
## Total locations
tourist_locations_wcoords_filepath <- file.path(datasets_dir, "Singapore Tourist Attractions.csv")
tourist_locations <- read_csv(tourist_locations_wcoords_filepath)
```
The first section of the back-end code involves reading in datasets using the LTA API. An example is shown below where we read in the ‘bus_stops’. We used a while loop for the skip_number because the inherent restriction is that only 500 lines can be read in at one time. Hence, we need to create a loop and bind all the rows together in order to retrieve the complete dataset. 

```{r Getting bus stops information}
if (!bus_stops_file_exists) {
  bus_stops_url <- "http://datamall2.mytransport.sg/ltaodataservice/BusStops"
  skip_number <- 0
  df <- data.frame() # Create an empty data frame to store the data

  while (TRUE) {
    url <- paste0(bus_stops_url, "?$skip=", skip_number)
    temp <- GET(url, add_headers(headers))
    res <- content(temp)

    temp_df <- do.call(rbind, res$value)
    temp_df <- as.data.frame(temp_df)
    if (nrow(temp_df) == 0) {
      break # Exit the loop if there's no more data
    }

    df <- rbind(df, temp_df) # Append the data to the main data frame
    skip_number <- skip_number + 500
  }

  flat_df <- unnest(df, cols = c(BusStopCode, RoadName, Description, Latitude, Longitude))
  write.csv(flat_df, file = bus_stops_filepath, row.names = FALSE) # Save the complete data frame as 'bus_stops.csv'
  print("File downloaded as bus_stops.csv")
} else {
  print("File exists")
}

bus_stops <- read_csv(bus_stops_filepath)
bus_stops
```

```{r Getting bus routes information}
## Bus Routes
bus_routes_filepath <- file.path(datasets_dir, "bus_routes.csv")
bus_routes_file_exists <- file.exists(bus_routes_filepath)

if (!bus_routes_file_exists) {
  bus_routes_url <- "http://datamall2.mytransport.sg/ltaodataservice/BusRoutes"
  skip_number <- 0
  df <- data.frame() # Create an empty data frame to store the data

  while (TRUE) {
    url <- paste0(bus_routes_url, "?$skip=", skip_number)
    temp <- GET(url, add_headers(headers))
    res <- content(temp)
    temp_df <- do.call(rbind, res$value)
    temp_df <- as.data.frame(temp_df)

    if (nrow(temp_df) == 0) {
      break # Exit the loop if there's no more data
    }

    df <- rbind(df, temp_df) # Append the data to the main data frame
    skip_number <- skip_number + 500
  }
  ## Add a flat_df function since the df are in lists of one to let them save into a csv
  flat_df <- unnest(df, cols = c(
    ServiceNo, Operator, Direction, StopSequence, BusStopCode, Distance, WD_FirstBus, WD_LastBus,
    SAT_FirstBus, SAT_LastBus, SUN_FirstBus, SUN_LastBus
  ))
  write.csv(flat_df, file = bus_routes_filepath, row.names = FALSE) # Save the complete data frame as 'bus_stops.csv'
} else {
  print("File exists")
}

bus_routes <- read_csv(bus_routes_filepath)
bus_routes

The ‘Bus Route’ LTA dataset is slightly counterintuitive to its name as it does not provide the list of intermittent bus stop names along a particular bus route, we can only infer the complete list of bus stops on one route from other variables provided such as ‘StopSequence’ and ‘BusStopCode’. Hence, in order to store that information locally for further manipulation and reduce the amount of query operations that we need to perform, we joined the ‘Bus Route’ and ‘Bus Stops’ datasets together based on the common variable “BusStopCode” to obtain a consolidated file named ‘Bus_Stops_WRoutes’. In order to keep our data structure lean, we only selected useful variables to keep, namely ‘ServiceNo’, ‘Direction’, ‘StopSequence’, ‘BusStopCode’, ‘Description’, ‘Latitude’ and ‘Longitude’. 

## local file to store the bus route of each bus
bus_routes_consolidated_filepath <- file.path(datasets_dir, "bus_stops_wroutes.csv")
bus_routes_consolidated_filepath_exists <- file.exists(bus_routes_consolidated_filepath)

if (!bus_routes_consolidated_filepath_exists) {
  consolidated_file <- bus_routes %>%
    left_join(bus_stops, by = "BusStopCode") %>%
    select(ServiceNo, Direction, StopSequence, BusStopCode, Description, Latitude, Longitude)

  write.csv(consolidated_file, file = "Bus_stops_wroutes.csv", row.names = FALSE)

  bus_stops_wroutes <- read_csv(bus_routes_consolidated_filepath)
} else {
  print("bus routes consolidated exists")
}

bus_stops_wroutes <- read_csv(bus_routes_consolidated_filepath)
```

The first function that we worked on is ‘calculate_distance’. After performing some desktop research, we decided to use the ‘distVincentySphere’ function by R that takes in the longitudinal and latitudinal coordinates of two points and returns the shortest distance between them. However, one limitation we need to note is that the distance that we calculate is not inclusive of distance across water bodies, hence, we left out tourist attractions in the Sentosa area. 


```{r calculate_distance function}
## Distance Function
calculate_distance <- function(row, lat, long) {
  point <- as.numeric(c(row["Longitude"], row["Latitude"]))
  distance <- distVincentySphere(point, c(long, lat))
  return(distance)
}
```

Next, we hope to find the nearest bus stops to the user in a 500m radius with the function ‘closest_bus_stop’. We take in the geographical coordinates of the user’s current location and apply the ‘calculate_distance’ on every row of ‘Bus_Stops_WRoutes’ and only save those whose distance calculation is less than or equal to 500m. With that, we return the bus stop that is the nearest to the user’s current location. 


```{r closest_bus_stop function}
## Finding nearest bus_stop in 500m
closest_bus_stop <- function(lat, long, bus_stops_wroutes) {
  temp <- as.data.frame(bus_stops_wroutes)
  temp$dist <- apply(temp, 1, function(row) calculate_distance(row, lat, long))
  ### Finds bus_stops in 500m radius
  # print(temp)
  ### Selecting closest bus stops for each bus
  wanted_bus_stops <- which(temp$dist <= 500)
  wanted <- temp[wanted_bus_stops, c("ServiceNo", "Direction", "BusStopCode", "Description", "dist")]
  ### Having only the closest distance busstop for each bus
  wanted <- wanted %>%
    group_by(ServiceNo, Direction) %>%
    slice_min(dist)

  return(wanted)
} 
```

Apart from making the application as easy to use as possible for the user, we also need to consider how fast the program can run on the backend. We know that too much querying will only increase the time taken to return the results and make our users wait unnecessarily. Therefore, further leveraging the function of ‘closest_bus_stop’, we created another dataset named ‘tourist_locations_wproximabusstops’ to include a column of ‘ProximalBusStops’ near each tourist attraction. We store the bus stops close to each tourist attraction in that column. This will save us efforts towards the end of the manipulation process as we just need to check if the alighting bus stops of the tourists fall into any row of this column. From there, we will be able to return the ultimate destination to the tourist. 

```{r creating tourist_locations_wproximalbusstops}
## Adding closest bus-stops to attractions to local file so it takes less time with api_calls later
tourist_locations_wproximalbusstops_filepath <- file.path(datasets_dir, "tourist_locations_wproximalbusstops.csv")
tourist_locations_wproximalbusstops_filepath_exists <- file.exists(tourist_locations_wproximalbusstops_filepath)

total_results_df <- data.frame(bus_stops = character())
if (!tourist_locations_wproximalbusstops_filepath_exists) {
  for (i in 1:nrow(tourist_locations)) {
    location <- tourist_locations[i, ]
    print(location)
    temp_df <- closest_bus_stop(as.numeric(location[4]), as.numeric(location[3]), bus_stops_wroutes)
    result_df <- data.frame(bus_stops = paste(unique(temp_df$BusStopCode), collapse = ","))
    total_results_df <- rbind(total_results_df, result_df)
  }
  tourist_locations$ProximalBusStops <- unlist(total_results_df)
  write.csv(tourist_locations, tourist_locations_wproximalbusstops_filepath, row.names = FALSE)
} else {
  print("tourist_locations_wproximalbusstops_name_exists")
}

tourist_locations_wproximalbusstops <- read_csv(tourist_locations_wproximalbusstops_filepath)
```

Moving on, we wrote a function on ‘bus_approaching’ to filter for buses in the closest_stops based on estimated arrival time (ETA). This function solely checks for whether the ETA is within the desired travelling time input given by the user.


```{r bus_approaching function}
# Function to filter buses in closest_stops based on estimated arrival time
bus_approaching <- function(row, headers, time_threshold) {
  bus_arrival_url <- "http://datamall2.mytransport.sg/ltaodataservice/BusArrivalv2"
  temp <- GET(bus_arrival_url, add_headers(headers),
    query = list(BusStopCode = row["BusStopCode"], ServiceNo = row["ServiceNo"])
  )
  res <- content(temp)
  if (length(res$Services) == 0) {
    return(FALSE)
  }
  # print(paste("Next Bus Estimated Arrival:", res$Services[[1]]$NextBus$EstimatedArrival, ";", "Seats Availability:", res$Services[[1]]$NextBus$Load))
  # print(as.POSIXct(res$Services[[1]]$NextBus$EstimatedArrival, format = "%Y-%m-%dT%H:%M:%S"))
  if (as.POSIXct(res$Services[[1]]$NextBus$EstimatedArrival, format = "%Y-%m-%dT%H:%M:%S") - Sys.time() < as.difftime(time_threshold, units = "mins")) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}
```

```{r Getting bus_stops_visited}
# Getting bus_stops_visited
bus_stops_visited <- function(bus_stops_wroutes, ServiceNo, Direction, BusStopCode, time_alloted) {
  ## Testing variables
  # ServiceNo = 174
  # Direction = 1
  # BusStopCode = 21161
  # time_alloted <- as.difftime(50, units = "mins")
  
  # print(BusStopCode)
  # print(time_alloted)
  bus_stops_reached <- list()
  running_total <- 0
  running_totals <- list()
  origin_time <- NULL
  OriginBusStopCode <- BusStopCode
  
  ## Check if no BusStops pass
  if (is.na(BusStopCode)){
    return(data.frame())
  }

  
  bus_stops_sequence <- bus_stops_wroutes[bus_stops_wroutes$BusStopCode == BusStopCode &
    bus_stops_wroutes$ServiceNo == ServiceNo, ]$StopSequence
  bus_stops_check <- bus_stops_wroutes[bus_stops_wroutes$ServiceNo == ServiceNo &
    bus_stops_wroutes$Direction == Direction &
    bus_stops_wroutes$StopSequence >= bus_stops_sequence, ]

  bus_arrival_url <- "http://datamall2.mytransport.sg/ltaodataservice/BusArrivalv2"
  # df_test <- list()

  # print(bus_stops_check)
  # Iterate through each bus's ETA, see if any bus_stops cannot arrive on time
  for (BusStopCode in bus_stops_check$BusStopCode) {
    # print(ServiceNo)
    # print(running_total)

    if (running_total <= time_alloted) {
      temp <- GET(bus_arrival_url, add_headers(headers),
        query = list(BusStopCode = BusStopCode, ServiceNo = ServiceNo)
      )
      res <- content(temp)
      if (length(res$Services) == 0) {
        return(NA)
      }
      res <- res$Services[[1]]

However, the team noticed the presence of edge cases along the way. There could be multiple buses of the same service no. drive in close time proximity to one another along the same bus route. Hence, we will not be able to ensure that the initial bus that we have recommended the user to take is indeed the bus reaching the alighting bus stop. There could be a bus in between the stop the tourist is at and the stop that is supposed to be next queried.

As there is no unique identifier of each bus since we are not given information like car plate number from the LTA, we have devised an improvised method to track the bus - by adding a running_total function. 

We take in the first timing (origin_time), which is the time when the current bus stop receives its first bus. Next, we make use of the running_total function to check if the next bus stop’s first bus ETA is earlier than the first bus ETA of the current stop, if so, that means there is the presence of a faster bus between the current bus stop and the next bus stop. Hence, we would use the second’s bus ETA instead and add that to our running total. Ultimately, this function serves the role of finding the estimated duration taken to take a user from point A to point B, regardless of which bus the user takes. 

Next, we return the ServiceNo, OriginalBusStopCode, BusStartTime and Load of the intermediate bus stops reached by the bus from point A to point B within designated time defined by the user. That way, we know where point B can potentially be given the user’s starting point at point A. 

      ## Gets first time
      if (is.null(origin_time)) {
        origin_time <- as.POSIXct(res$NextBus$EstimatedArrival, format = "%Y-%m-%dT%H:%M:%S")
        start_time <- origin_time
        bus_stops_reached <- rbind(bus_stops_reached, BusStopCode)
        running_totals <- rbind(running_totals, running_total)
        bus_load <- res$NextBus$Load
        # print(bus_load)
        # print(origin_time)
        next
      } else {
        time_diff <- difftime(as.POSIXct(res$NextBus$EstimatedArrival, format = "%Y-%m-%dT%H:%M:%S"), origin_time, units = "mins")
        # Check if the time difference is within the acceptable range
        if (time_diff >= as.difftime(30, units = "secs")) {
          # print(time_diff)
          origin_time <- as.POSIXct(res$NextBus$EstimatedArrival, format = "%Y-%m-%dT%H:%M:%S")
          running_total <- running_total + time_diff
        } else {
          time_diff <- difftime(as.POSIXct(res$NextBus2$EstimatedArrival, format = "%Y-%m-%dT%H:%M:%S"), origin_time, units = "mins")
          # print(time_diff,1)
          origin_time <- as.POSIXct(res$NextBus$EstimatedArrival, format = "%Y-%m-%dT%H:%M:%S")
          running_total <- running_total + time_diff
        }
        bus_stops_reached <- rbind(bus_stops_reached, BusStopCode)
        running_totals <- rbind(running_totals, running_total)
      }
    } else {
      break
    }
  }
  bus_stops_reached_wtime <- cbind(as.data.frame(bus_stops_reached), as.data.frame(running_totals))
  names(bus_stops_reached_wtime) <- c("BusStopCode", "ETA")

  bus_stops_reached_wtime <- bus_stops_reached_wtime %>%
    filter(ETA <= time_alloted)

  bus_stops_reached_wtime$ServiceNo <- ServiceNo
  bus_stops_reached_wtime$OriginBusStopCode <- OriginBusStopCode
  bus_stops_reached_wtime$BusStartTime <- start_time
  bus_stops_reached_wtime$Load <- bus_load

  return(bus_stops_reached_wtime)
}

```

Going along the same logic, we need to check for tourist locations reached. We focus on variables including ‘BusStopCode’, ‘ETA’, ‘ServiceNo’, ‘OriginBusStopCode’, ‘BusStartTime’, ‘Load’.

```{r checking for tourist location matches}
tourist_location_check <- function(tourist_locations_wproximalbusstops, bus_stops, bus_stops_reached_all) {
  tourist_location_reached_mod <- data.frame()
  for (i in 1:nrow(bus_stops_reached_all)) {
    bus_stop <- bus_stops_reached_all[i, ]
    matching_rows <- which(grepl(bus_stop[[1]], tourist_locations_wproximalbusstops$ProximalBusStops))
    tourist_location_reached <- tourist_locations_wproximalbusstops[matching_rows, ]
    tourist_location_reached$BusStopCode <- bus_stop[[1]]
    tourist_location_reached$ETA <- bus_stop[[2]]
    tourist_location_reached$ServiceNo <- bus_stop[[3]]
    tourist_location_reached$OriginBusStopCode <- bus_stop[[4]]
    tourist_location_reached$BusStartTime <- bus_stop[[5]]
    tourist_location_reached$Load <- bus_stop[[6]]
    tourist_location_reached_mod <- rbind(tourist_location_reached_mod, tourist_location_reached)
  }

  tourist_location_reached_mod$BusStopCode <- as.character(tourist_location_reached_mod$BusStopCode)
  tourist_location_reached_mod$ETA <- as.double(tourist_location_reached_mod$ETA)
  tourist_location_reached_mod$ServiceNo <- as.character(tourist_location_reached_mod$ServiceNo)
  tourist_location_reached_mod$OriginBusStopCode <- as.character(tourist_location_reached_mod$OriginBusStopCode)
  tourist_location_reached_mod$Load <- as.character(tourist_location_reached_mod$Load)
  
  tourist_location_reached_mod_ordered <- tourist_location_reached_mod %>%
    select(-ProximalBusStops) %>%
    inner_join(bus_stops, by = c(BusStopCode = "BusStopCode")) %>%
    select(-RoadName) %>%
    rename(
      DestinationLatitude = Latitude.x,
      DestinationLongitude = Longitude.x,
      DestinationBusStopCode = BusStopCode,
      DestinationBusStopName = Description,
      DestinationBusStopLatitude = Latitude.y,
      DestinationBusStopLongitude = Longitude.y
    ) %>%
    inner_join(bus_stops, by = c(OriginBusStopCode = "BusStopCode")) %>%
    select(-RoadName) %>%
    rename(
      OriginBusStopName = Description,
      OriginBusStopLatitude = Latitude,
      OriginBusStopLongitude = Longitude
    ) %>%
    mutate(BusEndTime = BusStartTime + as.difftime(ETA, unit = "mins")) %>%
    group_by(Destination) %>%
    mutate(ETA_min = min(BusEndTime)) %>%
    ungroup() %>%
    filter(ETA_min == BusEndTime) %>%
    select(-ETA_min) %>%
    mutate(TravelMode = ifelse(BusStartTime == BusEndTime, "Walk", "Bus")) %>%
    group_by(Destination) %>%
    slice(1)


  return(tourist_location_reached_mod_ordered)
}
```

Last but not least, we use ‘wanted_attractions’ which encompasses the usage of the functions that we have discussed above. We use closest_stops to find out the bus stops closest to the user in terms of distance. Among these bus stops returned, we filter for bus stops that have buses arriving in 5 minutes time. Next, we compare bus_stops_reached with bus stops that are near the tourist attractions. If they match, we return these attractions to the user.


```{r wanted_attractions function}
wanted_attractions <- function(lat, long, wanted_types, time_interval) {
  ## Required data
  # api_key <- "3x+HF5oTQ0eDUnVeFjakIQ=="
  # headers <- c(AccountKey = api_key)
  # bus_stops_wroutes <- read_csv("bus_stops_wroutes.csv")
  # tourist_locations_wproximalbusstops <- read_csv("tourist_locations_wproximalbusstops.csv")
  bus_stops_reached_all <- data.frame()

  ## Function calls
  ## Getting closest stops to user
  closest_stops <- closest_bus_stop(lat, long, bus_stops_wroutes)

  ## Checking for bus in 5 minutes
  closest_stops$approaching <- apply(closest_stops, 1, function(row) bus_approaching(row, headers, 5))
  closest_stops <- closest_stops[closest_stops$approaching == TRUE, ]

  ## Checking what busstops have been reached
  for (i in 1:nrow(closest_stops)) {
    row <- closest_stops[i, ]
    bus_stops_reached <- bus_stops_visited(bus_stops_wroutes, row$ServiceNo, row$Direction, row$BusStopCode, 
                                           as.difftime(time_interval - 10,unit = "mins"))
    # print(bus_stops_reached)
    bus_stops_reached_all <- rbind(bus_stops_reached_all, bus_stops_reached)
  }
  # Filtering bus_stops that don't pass criteria
  bus_stops_reached_all <- bus_stops_reached_all %>%
    filter(if_any(everything(), ~ !is.na(.)))

  ## Checking which tourist_location is Ok
  all_attractions <- (tourist_location_check(tourist_locations_wproximalbusstops, bus_stops, bus_stops_reached_all))
  all_attractions_filtered <- all_attractions %>%
    filter(Type %in% wanted_types)

  return(all_attractions_filtered)
}
```
FUTURE PROJECTS:
- Multi-bus routes
- Curating more attractions
- MRT when API is available
